%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% \usepackage{tgheros}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}
% \usepackage{helvet}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Siba Prasad Tripathy} \\ \vspace{1pt}
    \small +91-78942-31432 $|$ \href{mailto:sibatripathy19@gmail.com}{\underline{sibatripathy19@gmail.com}} $|$ 
    \href{https://linkedin.com/in//siba-prasad-tripathy}{\underline{linkedin.com/in/siba-prasad-tripathy}} $|$
    \href{https://github.com/siba-tripathy}{\underline{github.com/siba-tripathy}}
\end{center}

%
%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, JavaScript, Go} \\
     \textbf{Frameworks}{: Spring, Node.js, React, JUnit+Mockito, OAuth 2.0, GraphQL API} \\
     \textbf{Infra:}{ [AWS] EC2-ECS, Lambda, DymanoDB, ElasticSearch, ElastiCache, SQS-SNS, VPC, Route53, CloudWatch, CDK} \\
     \textbf{Developer Tools}{: Git, Docker, VS Code, IntelliJ, PostMan, SQL, vim, CI/CD pipelines} \\
     \textbf{Problem Solving}{: Algorithms, Data Structures, Design Patterns}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Engineer 2}{July 2022 ----- Present}
      {Amazon}{}
      \resumeItemListStart
        \resumeItem{Building ``Localization and Accessibility" marketplace with auto-dubbing workflow, compliance-edits, third-party vendor on-boarding/order/costing workflows, asset quality-checks and catalog ingestion into ``Prime Video Media Pipeline". Designed back-end systems, data models, both sync APIs and async event-driven architectures for efficient order fulfillment.}
        \resumeItem{Drove transcription of 1.5 million titles in regional languages(jp animes) into english for world-wide release with 30-day timeline by scaling order orchestration and model hosting services . Added search functionality in the portal for better user search experience.}
        \resumeItem{Added 60\% efficiency in localization turn-around time by automating vendor asset delivery via an FTP client, syncing external catalog services with localization service for notifications and escalation workflows.}
        \resumeItem{Influencing/brain-storming with product stakeholders on product roadmap, disambiguating customer journeys.}
        \resumeItem{Hiring and mentoring juniors, reviewing designs and code PRs, driving team ops review meetings, On-Call duties}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Development Engineer 1}{July 2019 -- June 2022}
      {Amazon}{}
      \resumeItemListStart
        \resumeItem{Implemented Migration of external Amazon Studios' 1P APIs from dedicated APIs to generic, federated GraphQL APIs. Achieved this by developing a new gradle build client library, using ApolloKotin libraries. This client builder was adopted by multiple external teams across Amazon.}
        \resumeItem{Designed and implemented role-based access control for security by introducing fine-grained authorization.}
        \resumeItem{Enabled creative Quality Check workflows for non English titles that make up 1/3rd of total 700K+ titles in goal}
        \resumeItem{Amazon Internal OAuth 2.0 implementation in \emph{Native AWS} services. Involved exploration and experimentation.}
        \resumeItem{Data Warehousing and Analytics for visualizing platform effectiveness, powered by AWS Redshift and Grafana for dashboards. Shipped complete ETL automated workflows and created SOPs for handling operational issues.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{Feb 2019 -- July 2019 }
      {Amazon Prime Video}{}
      \resumeItemListStart
        \resumeItem{Built a metadata-text translation solution, which enabled multiple internal teams to utilize external localization for their content, using existing localization and pricing system.}
        \resumeItem{Adoption by multiple teams is smooth running since \>3.5 years, with minor maintenance.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Cross Domain Search} $|$ \emph{TypeScript, ElasticSearch, Java, AWS SDK}}{Aug 2022 -- Nov 2022}
          \resumeItemListStart
            \resumeItem{Developed a ElasticSearch powered search application with cross domain search.}
            \resumeItem{Setup Cognito based authentication mechanism to enable developers to login to the ES domain and do administrative work like re-indexing, backfill, index analyzer changes.}
            \resumeItem{Added kibana based visualizations as a fast solution before implementing the fuull fledged Redshift based data warehousing setup with AWS QuickSight as auto refreshing dashboards.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Simple Space Shooting Game} $|$ \emph{JavaScript, HTML, CSS, Canvas APIs}}{May 2018 -- July 2019}
          \resumeItemListStart
            \resumeItem{Played around with HTML, JavaScript, interactive UI Canavs components in undergrad.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering} {July 2015 -- May 2019}
      {KIIT University [G.P.A - 8.9/10] }{Odisha}
    \resumeSubheading
      {12th Senior Secondary}{Jun 2013 -- May 2015}
      {St. Mary's School [92.00\%]}{Deepshikha}
      
  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
